Framework for Unified Optimal Synthesis of Planar Mechanisms for Motion and Path Generation using Shape Optimization

### 2018-03-10 idetc2018.tex
added overall layout figure

%%% Replace here with information related to your conference
\confshortname{IDETC/CIE 2017}
\conffullname{the ASME 2017 International Design Engineering Technical Conferences \&\\
              Computers and Information in Engineering Conference}

%%%%% for date in a single month, use
\confdate{26-29}
\confmonth{August}
%%%%% for date across two months, use
\confyear{2017}
\confcity{Quebec City}
\confcountry{Canada}

%%% Replace DETC2009/MESA-12345 with the number supplied to you
%%% by ASME for your paper.
\papernum{DRAFT: DETC2017-TBD}

@@

@@

Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively.), 3) novel algorithm for partial matching of motions , 4) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
In contrast to precision point method where distance measure is in terms of interpolation error, the distance measure of dissimilarity is valid between two planar curves or motions.
Which inherently requires the continuity of output; ensuring the output mechanism defect free throughout the task.

@@

A Hierarchy is created in the database by means of clustering, where top level comprises of few data points called cluster centers which are representative of the cluster points in the lower levels.
When a inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for k nearest neighbors among cluster centers in the database.
The neighbor is defined as motion or path whose part has a similar signature to the input. These k neighbors if needed, are subjected to fine tuning by local optimization to obtain set of solutions. Overall method is presented in algorithm~\ref{alg_overall}.

@@

\begin{algorithm}
    \SetKwInOut{Input}{Input}
    \SetKwInOut{Output}{Output}
    \Input{Twice Differentiable Parametric Representation of Motion $(x:x(t), y:y(t), \theta:\theta(t))$}
    \Output{signature //discretized signal in form of an array}
    k(t) = ComputeCurvature(x, y) using eq.~\ref{computeCurvature} \\
    K(t) = IntergrateCumulatively(k) using eq.~\ref{kInt} \\
    motionSignature = [] \\
    pathSignature = [] \\
    \For{$i = 0 \to max(K)$}
    {
      tmp = (value of t corresponding to which K has value i) \\
      $i = i + 0.1$ \\
      motionSignature.push(k(tmp)) \\
      pathSignature.push(k(tmp))
    }
    \Return{PathSignature, MotionSignature}
    \caption{Calculate Invariant Signatures}
    \label{alg_signature}
\end{algorithm}

Curvature of the path of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ given by,
\begin{eqnarray}
  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}} \label{curvature}\\
  K(t) = \int^{t}_0 |k(t)| \label{kInt},
\end{eqnarray}
where $\dot{x}$, $\ddot{x}(t)$ are first and second order derivative w.r.t. parameter t.
For an example, parametric motion could be a B-spline motion as shown in fig~\ref{bsplineFitting}.
We compute the curvature of path along the direction of t, using eq.~\ref{curvature} and the cumulative integral by eq.~\ref{kInt}.
For implementation purposes, we use scipy\cite{scipy} module for computations of B-splines and their derivatives.
Figure~\ref{curvatureK} shows computed curvatures and its unsigned integral of coupler path shown in Fig.~\ref{bsplineFitting}.
It can be seen that curvature is very low at start, increases as the curve bends along the path and drops once again as the path straightens out.
It is obvious that curvature plot will reverse if the direction of parameterization reverses.

@@

\subsection{Partial Matching of Path Signatures}\label{sec_ncc}
When a path query is raised, it can be very useful to know whether this path already exists as a part in some other path present in the database.
This subsection presents a method for determining this partial similarity.
Let $p$ be motion signature of such a part path which acts as template while $W$ is the motion signature corresponding to a path (Whole) that can completely embed the template as shown in Fig.~\ref{wholePart}. The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching. It will be used later for matching of motion signature.
The way this partial matching works is as follows:

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_path_signatures.eps}
  \caption{The domain of path signature is scale invariant but the range still has a scaling factor, which is taken by normalized cross-correlation.}
\label{pathSignature}
\end{figure}

>>>>

%%% Replace here with information related to your conference
\confshortname{IDETC/CIE 2018}
\conffullname{the ASME 2018 International Design Engineering Technical Conferences \&\\
              Computers and Information in Engineering Conference}

%%%%% for date in a single month, use
\confdate{26-29}
\confmonth{August}
%%%%% for date across two months, use
\confyear{2018}
\confcity{Quebec City}
\confcountry{Canada}

%%% Replace DETC2009/MESA-12345 with the number supplied to you
%%% by ASME for your paper.
\papernum{DRAFT: DETC2018-TBD}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figure/overall_approach.eps}
  \caption{General Layout of the approach.}
\label{overallMethod}
\end{figure*}

@@

Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively), 3) novel algorithm for partial matching of motions , 4) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
In contrast to precision point method where distance measure is in terms of interpolation error, the distance measure of dissimilarity is valid between two planar curves or motions.
Which inherently requires the continuity of output; ensuring the output mechanism defect free throughout the task.

@@

A Hierarchy is created in the database by means of clustering, where top level comprises of few data points called cluster centers which are representative of the cluster points in the lower levels.
When a inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for k nearest neighbors among cluster centers in the database.
The neighbor is defined as motion or path whose part has a similar signature to the input. These k neighbors if needed, are subjected to fine tuning by local optimization to obtain set of solutions. Overall method is given in algorithm~\ref{alg_overall} and depicted in Fig.~\ref{overallMethod}.

@@

\begin{algorithm}
    \SetKwInOut{Input}{Input}
    \SetKwInOut{Output}{Output}
    \Input{Twice Differentiable Parametric Representation of Motion $(x:x(t), y:y(t), \theta:\theta(t))$}
    \Output{signature //discretized signal in form of an array}
    k(t) = ComputeCurvature(x, y) using eq.~\ref{curvatureEq} \\
    K(t) = IntergrateCumulatively(k) using eq.~\ref{kInt} \\
    motionSignature = [] \\
    pathSignature = [] \\
    \For{$i = 0 \to max(K)$}
    {
      tmp = (value of t corresponding to which K has value i) \\
      $i = i + 0.1$ \\
      motionSignature.push(k(tmp)) \\
      pathSignature.push(k(tmp))
    }
    \Return{PathSignature, MotionSignature}
    \caption{Calculate Invariant Signatures}
    \label{alg_signature}
\end{algorithm}

Curvature of the path of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ given by,
\begin{eqnarray}
  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}} \label{curvatureEq}\\
  K(t) = \int^{t}_0 |k(t)| \label{kInt},
\end{eqnarray}
where $\dot{x}$, $\ddot{x}(t)$ are first and second order derivative w.r.t. parameter t.
For an example, parametric motion could be a B-spline motion as shown in fig~\ref{bsplineFitting}.
We compute the curvature of path along the direction of t, using eq.~\ref{curvature} and the cumulative integral by eq.~\ref{kInt}.
For implementation purposes, we use scipy\cite{scipy} module for computations of B-splines and their derivatives.
Figure~\ref{curvatureK} shows computed curvatures and its unsigned integral of coupler path shown in Fig.~\ref{bsplineFitting}.
It can be seen that curvature is very low at start, increases as the curve bends along the path and drops once again as the path straightens out.
It is obvious that curvature plot will reverse if the direction of parameterization reverses.

@@

\subsection{Partial Matching of Path Signatures}\label{sec_ncc}
When a path query is raised, it can be very useful to know whether this path already exists as a part in some other path present in the database.
This subsection presents a method for determining this partial similarity.
Lets consider two coupler paths as shown in~\ref{wholePart}.
Let $p$ be path signature of such a part path which acts as template while $W$ is the path signature corresponding to a path (Whole) that can completely embed the template as shown in Fig.~\ref{pathSignature}. The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching. It will be used later for matching of motion signature.
The way this partial matching works is as follows:

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_path_signatures.eps}
  \caption{Path Signatures of part $p$ and whole $W$ from Fig.~\ref{wholePart}.The domain of path signature is scale invariant but the range still has a scaling factor, which is taken care by normalized cross-correlation.}
\label{pathSignature}
\end{figure}
